### 2015-10-16 locking.tex
minor fixes

We believe that the first interpretation is the more natural one, as it does not make much sense to allocate resources to tasks that cannot yet use them. However, for the sake of completeness, we show that either interpretation can lead to deadline misses even if the task set trivially schedulable without any enforcement.

>>>>

We believe that the first interpretation is the more natural one, as it does not make much sense to allocate resources to tasks that cannot yet use them. However, for the sake of completeness, we show that either interpretation can lead to deadline misses even if the task set is trivially schedulable without any enforcement.

### 2015-10-16 untitled.tex
minor fixes

The period enforcer algorithm is worth a second look for a number of reasons. First, in the words of Rajkumar, it ``forces tasks to behave like ideal periodic tasks from the scheduling point of view with no associated scheduling penalties''~\cite{Raj:suspension1991}, which is obviously highly desirable in many practical applications in which self-suspensions are inevitable (e.g., when offloading computations to co-processors such as GPUs or DSPs). Second, the later-proposed, but more widely-known \emph{released guard} algorithm~\cite{SL:96} uses a technique quite similar to period enforcement to control scheduling penalties due to release jitter in distributed systems. The period enforcer algorithm has also attracted growing attention  and has been mentioned in several recent works  (e.g.,~\cite{LNR:09,LR:10,Lak:11,LC:14,KANR:13,HY:11,CA:09,CA:10,CA:10b}), at times controversially~\cite{BA:08a}. And last but not least, the period enforcer algorithm plays a significant role in Rajkumar's seminal book on   real-time  synchronization~\cite{Raj:91}.

@@

\subsection{Questions answered in this paper}
\label{sec:questions}

>>>>

The period enforcer algorithm is worth a second look for a number of reasons. First, in the words of Rajkumar, it ``forces tasks to behave like ideal periodic tasks from the scheduling point of view with no associated scheduling penalties''~\cite{Raj:suspension1991}, which is obviously highly desirable in many practical applications in which self-suspensions are inevitable (e.g., when offloading computations to co-processors such as GPUs or DSPs). Second, the later-proposed, but more widely-known \emph{released guard} algorithm~\cite{SL:96} uses a technique quite similar to period enforcement to control scheduling penalties due to release jitter in distributed systems. The period enforcer algorithm has also attracted renewed attention in recent years and has been discussed in several current works  (e.g.,~\cite{LNR:09,LR:10,Lak:11,LC:14,KANR:13,HY:11,CA:09,CA:10,CA:10b}), at times controversially~\cite{BA:08a}. And last but not least, the period enforcer algorithm plays a significant role in Rajkumar's seminal book on   real-time  synchronization~\cite{Raj:91}.

@@

\subsection{Questions Answered in This Paper}
\label{sec:questions}
